Flux2022

### 2022-04-05 Flux2022.Rmd
add gitdro submodule

library(tidyverse)
library(psych )
```

@@

@@

summary(baseline_cognition_1)
summary(baseline_cognition_2)
```

>>>>

library(tidyverse)
library(psych)
library(sjPlot)
```

@@

#Cognition fluid
baseline_cognition_fluid_1 <- lm(corrected_gap ~ nihtbx_fluidcomp_agecorrected, data=sample_1)
baseline_cognition_fluid_2 <- lm(corrected_gap ~ nihtbx_fluidcomp_agecorrected, data=sample_2)

#Cognition crystallized
baseline_cognition_crystal_1 <- lm(corrected_gap ~ nihtbx_cryst_agecorrected, data=sample_1)
baseline_cognition_crystal_2 <- lm(corrected_gap ~ nihtbx_cryst_agecorrected, data=sample_2)
```

@@

summary(baseline_cognition_1)
summary(baseline_cognition_2)

summary(baseline_cognition_fluid_1)
summary(baseline_cognition_fluid_2)

summary(baseline_cognition_crystal_1)
summary(baseline_cognition_crystal_2)

Model Figures
```{r}
plot_model(baseline_puberty_y_mean_1, type="pred", terms = "youth_mean")

plot_model(baseline_puberty_p_mean_1, type="pred", terms = "parent_mean")

plot_model(baseline_cognition_1, type="pred", terms = "nihtbx_totalcomp_agecorrected")
plot_model(baseline_cognition_2, type="pred", terms = "nihtbx_totalcomp_agecorrected")
